Merging Datasets Through Deep learning

### 2018-09-02 paper2018/evaluation.tex
added latest numbers

\begin{table*}[ht]
\caption{Results for people and companies by loss functions}
\label{Evaluation}
\begin{tabular}{l|l|r|r|r|r|r|r|r|r|}
\hline
Entity Type & Loss Function & Recall & Precision@1 & Precision \\
\hline
\multirow{4}{*}{People} & Our loss & .81 & .93 & .69 & .53 & 21.08 & 2.39 & 1.27 & 33.46 \\
\hline
& Triplet loss & .73 & .91 & .38 & .13 & .84 & .54 & .1 & .86 \\
\hline
& Improved loss & NA & NA & NA & NA & NA & NA & NA & NA \\
\hline
& Angular loss & NA & NA & NA & NA & NA & NA & NA & NA \\
\hline
\multirow{4}{*}{Companies} & Our loss & NA & NA & NA & NA & NA & NA & NA & NA \\
& Triplet loss & NA & NA & NA & NA & NA & NA & NA & NA \\
\hline
& Improved loss & NA & NA & NA & NA & NA & NA & NA & NA \\
\hline
& Angular loss & NA & NA & NA & NA & NA & NA & NA & NA \\
\hline
\end{tabular}
\end{table*}

>>>>

\begin{table*}[ht]
\caption{Precision and Recall for people and companies by loss functions}
\label{Evaluation}
\begin{tabular}{l|l|r|r|r|}
\hline
Entity Type & Loss Function & Recall & Precision@1 & Precision \\
\hline
\multirow{4}{*}{People} & Adapted loss & .81 & .81 & .63 \\
\hline
& Triplet loss & .74 & .84 & .55 \\
\hline
& Improved loss & .71 & .52 & .45 \\
\hline
& Angular loss & .04 & .09 & .02 \\
\hline
\multirow{4}{*}{Companies} & Adapted loss & .72 & .73 & .64 \\
& Triplet loss & .75 & .76 & .67 \\
\hline
& Improved loss & .74 & .72 & .64 \\
\hline
& Angular loss & NA & NA & NA \\
\hline
\end{tabular}
\end{table*}

\begin{table*}[ht]
\caption{Distance estimates for people and companies after training}
\label{Evaluation}
\begin{tabular}{l|l|r|r|r|r|}
\hline
Entity Type & Loss Function & Mean Pos & Std Pos & Mean Neg & Std Neg \\
\hline
\multirow{4}{*}{People} & Adapted loss & 1.59 & 4.04 & 2.44 & 2.45 \\
\hline
& Triplet loss & .46 & .18 & .55 & .10 \\
\hline
& Improved loss & .15 & .38 & .21 & .18 \\
\hline
& Angular loss & .51 & .25 & .06 & .02 \\
\hline
\multirow{4}{*}{Companies} & Adapted loss & 2.38 & 3.77 & 3.23 & 1.71 \\
& Triplet loss & .39 & .28 & .55 & .09 \\
\hline
& Improved loss & .32 & .50 & .42 & 0.19 \\
\hline
& Angular loss & NA & NA & NA & NA \\
\hline
\end{tabular}
\end{table*}
